### 2025-11-25 CV2/awards.tex
CV

\section{Honors and Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{enumerate}
	\item  \textbf{CEMSE Student Research Excellence Award}, King Abdullah University of Science and Technology, 2021
	\item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
	\item \textbf{Abramov’s Fund Scholarship for Excellence in Study}, Moscow Institute of Physics and Technology, 2015-2017
	\item \textbf{Asian Physics Olympiad (APhO) 2014, Honourable Mention}, Singapore (participated as a member of Russian national team)

>>>>

\section{Honors and Awards}
\hypersetup{breaklinks,urlcolor=black,linkcolor=black}
\begin{enumerate}
  \item  \href{https://ai-awards.ru}{\textbf{National Award ``AI Leaders'' 2025}}, \href{https://aij.ru/en}{AI Journey 2025 Conference}
  \item \href{https://media.innopolis.university/news/yandex-research-employee-receives-polyak-prize/}{\textbf{Boris Polyak Scientific Prize for Young Researchers 2025}}, Innopolis University
  \item  \textbf{CEMSE Student Research Excellence Award}, King Abdullah University of Science and Technology, 2021
  \item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
  \item \href{https://yandex.com/scholarships/#laureates}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
  \item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
  \item \href{https://yandex.com/scholarships/#laureates}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
  \item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
  \item \textbf{Abramov’s Fund Scholarship for Excellence in Study}, Moscow Institute of Physics and Technology, 2015-2017
  \item \textbf{Asian Physics Olympiad (APhO) 2014, Honourable Mention}, Singapore (participated as a member of Russian national team)
